\documentclass{article}

\usepackage{graphicx}
\usepackage{url}

\title{Progress Report}
\author{James Lee\\
	\small Computer Science and Electrical Engineering\\
	\small University of Maryland Baltimore County\\
	\small\tt jlee23@umbc.edu}
\date{March 23, 2008}

\begin{document}
\maketitle

\section*{Progress}
So far I have completed a written specification of the P2P protocol that I will implement on top of Tor.  It contains the message formats between hubs and clients and recommendations on how such a system should be implemented.

It was difficult to come up with a robust protocol.  I'm sure I will be changing it as I implement it to make it more resilliant to malicious users.  I borrowed ideas from the (poorly documented) Direct Connect protocol until I can see how they actually work.

As far as the implementation goes, I have already been experimenting with ways to control Tor from Java.  Right now, the configuration is written out in code to a file, then Tor is started.  I would like to use the Tor control protocol as originally proposed to make the configuration more dynamic rather than using flat files.

I have also mocked up a user intereface for the client presenting a list of online users, a chat area, a search area, and a file transfer area.  The user interface does not currently do anything, though.

In the next two weeks I must complete the implementation of the hub and client.

\section*{Updated Schedule}
I missed a couple of my original milestones, but I think I have enough half-completed work that I can complete all my goals on the following dates comfortably.

\begin{center}
\begin{tabular}{ll}
\multicolumn{1}{c}{\bf Date} & \multicolumn{1}{c}{\bf Milestone}\\
\hline
March 16 & Protocols defined and documented\\
March 24 & Progress report\\
March 30 & Tor configuration library and hub complete\\
April 6 & Client, user interface and installer completed\\
April 14 & Complete draft report and draft presentation\\
April 21 & Final presentation\\
May 5 & Final report
\end{tabular}
\end{center}

\section*{Draft Report Outline}
\begin{description}
\item[Introduction] An overview of the paper.
\item[Motivation] This can be adapted from the project proposal.
\item[Previous Work] This can be adapted from the project proposal.
\item[Design Overview] A summary of the specification.
\item[Implementation Overview] A summary of the hub and client implementation of the specification.
\item[Analysis] A discussion of how the design and implementation solves the proposed problem.
\item[Conclusion] Wrap up the paper; discuss open problems.
\item[Appendix: Protocol Specification] An attached copy of one of the project's deliverables.
\end{description}

\nocite{dc-protocol}
\nocite{tor-ctl}
\nocite{tor-design}

\bibliographystyle{unsrturl}
\bibliography{progress}
\end{document}
